``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-31 paper/paper.tex
added section on LM style metric.  still need to incorporate in other sections, and compute aggregate scores.

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|r|}
    \hline
    & & Pearson's $\rho$ \\
    \hline
    \hline
    semantic adequacy & BLEU & 0.35 \\
    \hline
    dissimilarity & PINC & 0.78 \\
    \hline
    style & BLEU & 0.07 \\
    \hline
    style & PINC & 0.20 \\
    \hline
    style & Cosine & 0.37 \\
    \hline
    style & Logistic regression & 0.47 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Correlation between various human judgments and automatic evaluation metrics}
  \label{correlation}
\end{table}

>>>>

\subsection{Language Model Style Metric}
Another approach is to build seperate language models for text in the target style and outside the style, and apply Bayes' rule to estimate
the probability that a particular sentence was generated based on the style or not:
\begin{eqnarray*}
P(\text{style}=\text{target}|\text{sentence}) 
& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) P(\text{target})}{P(\text{sentence})} \\
& = & \frac{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5}{P_\text{LM}(\text{sentence}|\text{target}) \times 0.5 + P_\text{LM}(\text{sentence}|\text{source}) \times 0.5} \\
& = & \frac{P_\text{LM}(\text{sentence}|\text{target})}{P_\text{LM}(\text{sentence}|\text{target}) + P_\text{LM}(\text{sentence}|\text{source})} \\
\end{eqnarray*}

That is the probability that a sentence was generated according to the target style is simply it's probability according to the target language model divided by the sum of it's
probability according to the source and target language models.

@@

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l|r|r|}
    \hline
    & & $\rho$ (Annotator 1) & $\rho$ (Annotator 2) \\
    \hline
    \hline
    semantic adequacy & BLEU & 0.35 & 0.31 \\
    \hline
    dissimilarity & PINC & 0.78 & 0.82 \\
    \hline
    style & BLEU & 0.07 & 0.06 \\
    \hline
    style & PINC & 0.20 & 0.45 \\
    \hline
    style & Cosine & 0.37 & 0.41 \\
    \hline
    style & LM & 0.45 & 0.48 \\
    \hline
    style & Logistic regression & 0.47 & 0.48 \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Correlation between various human judgments and automatic evaluation metrics.  Pearson's correlation coefficient is displayed
  between the automatic metrics and human judgements from each annotator.}
  \label{correlation}
\end{table}
